The Inconsistency in G\"odel's Ontological Argument: \\ A Success Story for AI in Metaphysics

### 2016-02-01 Papers/InProgress/IJCAI/submission.tex
minor modifications

St. Anselm's ontological argument \cite{Proslogion} can be regarded as
the ancestor of modern ontological arguments such as G\"odel's. In the
millenium between Anselm and G\"odel, many philosophers modified and
arguably improved Anselm's argument. Of particular importance to
G\"odel was the work of Leibniz. 
%\cite{ToDo:Leibniz}.  
Although G\"odel's notion of positive property is not exactly the same as Leibniz's notion of perfection, G\"odel's manuscript
(Fig.~\ref{GoedelScript}) can be considered a translation of Leibniz's
presentation of the argument into modern modal logic. G\"odel
discussed his manuscript with Scott, who shared a slightly different
version with a larger public. Scott's version of the axioms and
definitions, formalized in Isabelle, is shown in
Fig.~\ref{Scott_S5U}. The main difference to G\"odel's version is an extra conjunct in the definition of \emph{essence}. G\"odel's
different definition of essence can be seen either in his manuscript
(Fig.~\ref{GoedelScript}) or, in more modern notation, in the Isabelle
formalization shown in Fig.~\ref{InconsistencyIsabelleK}. For Scott,
an essential property of an individual must be possessed by
him/her. For G\"odel, this is not required.

@@

The inconsistency verified in Fig.~\ref{InconsistencyIsabelleK} follows from the definition of
essence (ess), the definition of necessary existence (NE), the
axioms A1(a) and A2 (which entail theorem T1), and axiom A5. It remains to show that
these ingredients are actually present in G\"odel's manuscript in
Fig.~\ref{GoedelScript}.

>>>>

St. Anselm's ontological argument \cite{Proslogion} can be regarded as
the ancestor of modern ontological arguments such as G\"odel's. In the
millenium between Anselm and G\"odel, many philosophers modified and
arguably improved Anselm's argument. Of particular importance to
G\"odel was the work of Leibniz. 
%\cite{ToDo:Leibniz}.  
Although G\"odel's notion of positive property is not exactly the same as Leibniz's notion of perfection, G\"odel's manuscript
(Fig.~\ref{GoedelScript}) can be considered a translation of Leibniz's
presentation of the argument into modern modal logic. G\"odel
discussed his manuscript with Scott, who shared a slightly different
version with a larger public. Scott's version of the axioms and
definitions, formalized in Isabelle, is shown in
Fig.~\ref{Scott_S5U}. The main difference to G\"odel's version is an
extra conjunct in the definition of \emph{essence} (\emph{ess}). G\"odel's
different definition of essence can be seen either in his manuscript
(Fig.~\ref{GoedelScript}) or, in more modern notation, in the Isabelle
formalization shown in Fig.~\ref{InconsistencyIsabelleK}. For Scott,
an essential property of an individual must be possessed by
him/her. For G\"odel, this is not required.

@@

The inconsistency verified in Fig.~\ref{InconsistencyIsabelleK} follows from the definition of
essence (ess), the definition of necessary existence (NE), the
axioms A1a and A2 (which entail theorem T1), and axiom A5. It remains to show that
these ingredients are actually present in G\"odel's manuscript in
Fig.~\ref{GoedelScript}.
